\chapter{Introduction $\&$ Background } 
The purpose of the project is to create a Booming Bass, which produces a clear sound. For this project, our entire mentorate group has been divided into two groups. Each of these two groups consists of around ten students, which have been split up into several groups with various tasks. \\
The main objectives of the sound system are to boost the incoming signal, power the system, and filter the boosted signal, which will then be fed into the speakers. An image that provides an overview of these objectives has been included in chapter 2.2. \\

The tasks are distributed as such:
\begin{itemize}
    \item Power Supply: two students will work on supplying power to the rest of the circuit, such as the power amplifier.
    \item Power amplifier: three students will work on amplifying the input signal, such that it is easier to filter different frequencies. 
    \item High filter: two students will work on filtering out the low- and mid-range frequencies, such that the high-range speaker will only emit high-frequency sound waves.
    \item Low filter: two students will work on filtering out the high- and mid-range frequencies, such that the bass speaker will only emit low-frequency sound waves, also known as bass.
    \item Mid filter: two or three students will work on filtering out the high- and low-range frequencies, such that the mid-range speaker will only emit mid-frequency sound waves.
\end{itemize}
\\
The project will last ten weeks and a different chair and secretary will be appointed each week. The chair will lead the group and make sure the schedule is adhered to, and the secretary will take notes. We have been taught background information from the first semester of the study which we will apply in this project. We will learn more about the details, obstacles, and lessons involved with creating filters, supplies, and amplifiers as we go. Either through linear circuits B or through the lab assignments.
\\ \newline
At the end of the project, we will organize a meeting with the other subgroup to consider which individual components will make up the Booming Bass system. Considering the fact that our components have to be interchangeable with the other subgroup, we have to have regular meetings, where we make sure the values used in calculations are roughly the same.\\

