\chapter{Conclusion} 

The goal of this project is to construct an autonomous robot that is able to pass a set of challenges. It should be able to make its way through maze, using an on-board infrared sensor and the instructions given to it from an algorithm running on a computer. These instructions are to be passed to the robot via wireless communication.

\medskip
The workload has been split over multiple subgroups. There are four subgroups. The first of these is to write the hardware for a finite-state machine so the robot can detect obstacles in path. Another group is responsible for the serial communication between the computer and the robot. To do this, this group needs to write an application for a computer and the hardware for the robot. There is a different group responsible for writing the application that is to send instructions to the robot. These instructions are what will be used by the robot to make its way through the maze. The last group is responsible for making a sensor that can detect mines on the maze.

\medskip
This project has multiple limits. There is a time constraint and we are limited in our experience working on similar projects. This means that we lack both technical knowledge and communication skills. It is crucial to minimize the effects of these limits on our project in all ways possible. One way we limit the effect of our time constraint is by creating a schedule which gives an overview of what activities need to be completed at what time. This schedule has tasks per subgroup.

\medskip
Each of our limits also pose a risk. We have reviewed several risks with a high likelihood of occurring and how to counter or resolve the possible issues that might that might ensue. We have divided these risks into three categories. There are time-related risks, risks involving our time constraint, member related risks, risks relating to a team member not (properly) contributing to the project, and communication related risks, which may cause problems due to miscommunication.

\medskip
Our hope is that we will be able to bring this project to a good end. 
